Proposal to improve BBC Search through the use of Linked Data

### 2014-04-16 paper.tex
Made some headway with the introduction.

\title{}
\author{Ross Fenning}

@@

In more recent years, a growing trend has emerged to use
\emph{Linked Data} in the enterprise to remove the need
for repeated integration projects or data warehousing.
\cite{allemang2010semantic}

@@

\section{Curation}

@@

>>>>

\title{Proposal to improve BBC Search through the use of Linked Data}
\author{Ross Fenning}

@@

Some of the data is fairly flat, textual content such as articles and some
information -- such as programmes -- is very structured (e.g. programmes,
series, episodes, times of broadcast, channel on which they are broadcast,
what times they are available to watch on iPlayer, what kinds of devices
are permitted by rights to watch them on iPlayer). This has challenges
for providing a consistent and meaningful user experience across such
a heterogenous mix of content.

% Do we need this?
Concepts central to the information retrieval domain such as creating
tokenisation, stemming, lemmatisation and relevance
algorithms can normally be delgated to
third party proprietary or free software. It is still useful however
for developers of full search application to be aware of these concepts even
if their implementation is abstracted away. Tokenisation, stemming and
lemmatisation are index time concerns, the full definitions of which
are out of scope for this report. In short, we want a search application
to understand individual words within an article and to understand that, for
example, ``mice'' and ``mouse'' are approximately the same word as well
as verb forms like ``swim'', ``swam'', ``swum'' and ``swimming'' all being
equivalent in the context of keyword retrieval.

@@

\section{Editor's Choice}

\section{Search Suggest}

@@

\section{Linked Enterprise Data}

In recent years, a growing trend has emerged to use
\emph{Linked Data} in the enterprise to remove the need
for repeated integration projects or data warehousing.
\cite{allemang2010semantic} If we view the indexing processes
of a search application as a variant of data warehousing,
we can start to argue for enterprise-wide publishing of
linked data as a more cost effective means of building search
indexes over bespoke integration efforts.

An important consideration is that BBC Search is largely directing
users to public pages on the BBC website, a large number of which have
already published some of their metadata as linked data. Notably, BBC News,
BBC Sport and BBC Food all use some combination
of microformats, microdata, RDFa, HTML meta tags within their HTML content
pages. Some of this was to improve search results in external search engines
such as Google and some of it ties into Facebook's Open Graph Protocol, which
enables and enhances social media sharing of the pages.

These efforts are not as structured and rich as the more notable uses
of semantic web technologies on the programmes microsites, Nature and BBC
Music \cite{}, but indicate that some level of metadata can be retrieved
as linked data. In cases where the metadata are rich enough, it might be
possible to avoid direct integration with databases, hidden back end
web services and other structured ``feeds'' typically set up for enterprise
integration.
